---
title: "Puget Sound observed pH time series detiding"
author: "M. W. Beck"
output: html_document
---
  
```{r setup, warning = F, message = F}
library(knitr)
library(tidyverse)
library(readxl)
library(here)
library(lubridate)
library(janitor)
library(WtRegDO)

opts_chunk$set(warning = FALSE, message = FALSE)

# buoy, farm WDNR
obsdat1 <- read.csv(here('data/raw/2018 WDNR pH sensor data - 2018 WDNR pH sensor data.csv.csv')) %>% 
  select(Date, TimePST, BuoypHAG, MidpHP1) %>% 
  gather('loc', 'pH', -Date, -TimePST) %>% 
  mutate(
    loc = case_when(
      grepl('Buoy', loc) ~ 'WDNR Buoy', 
      grepl('Mid', loc) ~ 'WDNR Farm center'
    ), 
    loc = factor(loc, levels = c('WDNR Buoy', 'WDNR Farm edge', 'WDNR Farm center'))
  ) %>% 
  unite('datetime', Date, TimePST, sep = ' ') %>% 
  mutate(
    datetime = mdy_hms(datetime, tz = 'Pacific/Pitcairn')
  ) %>% 
  filter(as.Date(datetime) <= ymd('2018-07-07') & as.Date(datetime) >= ymd('2018-05-25')) %>% 
  filter(minute(datetime) == 0)

subdts <- ymd(c('2018-05-25', '2018-07-06'))

# SB1 1m
obsdat2 <- read.csv(here('data/raw/SB1_1m_PMEL_2017-2018.csv')) %>% 
  group_by(year, month, day, hour) %>% 
  sample_n(1) %>% # sometimes there's more than one measurement per hour
  ungroup %>% 
  unite('date', month, day, year, sep = '-') %>% 
  unite('time', hour, min, sec, sep = ':') %>% 
  unite('datetime', date, time, sep = ' ') %>% 
  mutate(
    datetime = mdy_hms(datetime, tz = 'UTC'), 
    datetime = with_tz(datetime, tz = 'Pacific/Pitcairn'),
    datetime = floor_date(datetime, unit = 'hour'),
    loc = 'SB1 1m'
  ) %>% 
  rename(pH = pH_tot) %>% 
  filter(as.Date(datetime) <= subdts[2] & as.Date(datetime) >= subdts[1])

# NB1 3m
obsdat3 <- read.csv(here('data/raw/NB1_3m_SeaFET001_pH_tot.csv')) %>% 
  group_by(year, month, day, hour) %>% 
  sample_n(1) %>% # sometimes there's more than one measurement per hour
  ungroup %>% 
  unite('date', month, day, year, sep = '-') %>% 
  unite('time', hour, min, sec, sep = ':') %>% 
  unite('datetime', date, time, sep = ' ') %>% 
  mutate(
    datetime = mdy_hms(datetime, tz = 'UTC'), 
    datetime = with_tz(datetime, tz = 'Pacific/Pitcairn'),
    datetime = floor_date(datetime, unit = 'hour'),
    loc = 'NB1 3m'
  ) %>% 
  rename(pH = pH_tot) %>% 
  filter(as.Date(datetime) <= subdts[2] & as.Date(datetime) >= subdts[1])

# combine
obsdat <- bind_rows(obsdat1, obsdat2, obsdat3)

# tidal data from ADCP
tiddat <- read.csv(here('data/raw/SL1_Lander_depth_UTC.csv')) %>%
  unite('datetime', year, month, day, hour, min, sec) %>% 
  # clean_names() %>%
  rename( 
    Tide = depth
  ) %>% 
  mutate(
    datetime = ymd_hms(datetime), 
    datetime = with_tz(datetime, tzone = 'Pacific/Pitcairn')
  ) %>% 
  filter(minute(datetime) == 0 & second(datetime) == 0) %>% 
  filter(datetime >= min(obsdat$datetime) & datetime <= max(obsdat$datetime))

# combine ph and tidal data
alldat <- obsdat %>% 
  full_join(tiddat, by = 'datetime') %>% 
  rename(DateTimeStamp = datetime) 

lat <- 47.87167
long <- -122.60491
tz <- 'Pacific/Pitcairn'

dtdres <- alldat %>% 
  group_by(loc) %>% 
  nest() %>% 
  mutate(
    dtd = purrr::map(data, function(x){
      
      dtd <- wtreg(x, parallel = F, wins = list(8, 3, 0.7), DO_obs = 'pH', 
                   tz = tz, lat = lat, long = long)
      
      out <- dtd %>% 
        select(
          DateTimeStamp, 
          metab_date,
          pH = DO_obs, 
          pH_dtd = DO_nrm
        ) %>% 
        gather('var', 'val',  -DateTimeStamp, -metab_date) 
      
      return(out)
      
    })
  ) %>% 
  select(loc, dtd) %>% 
  unnest('dtd')
```

This plot provides an indication of when detiding may not be effective, shown as a moving window correlation of change in tide vs sun angle. Large negative or positive correlations show when the two are confounded and when detiding may remove too much biological signal of productivity. This can be interpreted relative to the wavelet scalogram (left: pH signal is out of phase with tide, right: pH and tide signals are in phase with each other, down: tide signal leads the pH signal, up: pH signal leads the tide signal).

```{r, fig.height = 2, fig.width = 8}
tochk <- alldat %>% 
  select(DateTimeStamp, Tide) %>% 
  unique
evalcor(tochk, tz = tz, lat = lat, long = long, harm = F)
```

Plots of observed pH (red) and detided pH (blue), by location. 

```{r, fig.height = 7, fig.width = 9}
ggplot(dtdres, aes(x = DateTimeStamp, y = val, color = var)) +
  geom_line() +
  facet_wrap(~loc, ncol = 1, scales = 'free_y') +
  theme_minimal() + 
  labs(
    y = 'pH', 
    x = NULL, 
    color = NULL
  )
```

Plots of diel pH range for observed pH (top) and detided pH (bottom), by locatin.

```{r, fig.height = 4, fig.width = 9}
dtdsum <- dtdres %>% 
  group_by(loc, metab_date, var) %>% 
  summarise(
    rng = diff(range(val, na.rm = T)), 
    ave = mean(val, na.rm = T),
    .groups = 'drop'
  )

ggplot(dtdsum, aes(x = metab_date, y = rng, color = loc)) +
  geom_line(size = 1) + 
  facet_wrap(~var, ncol = 1, scales = 'free_y') +
  theme_minimal() + 
  labs(
    x = NULL, 
    y = 'daily pH range', 
    color = NULL
  )

ggplot(dtdsum, aes(x = metab_date, y = ave, color = loc)) +
  geom_line(size = 1) + 
  facet_wrap(~var, ncol = 1, scales = 'free_y') +
  theme_minimal() + 
  labs(
    x = NULL, 
    y = 'daily pH average', 
    color = NULL
  )

```
