---
output: 
  html_document:
    code_folding: hide
    css: styles.css
---
  
# Evaluation of oyster exposure experiments {.tabset}
  
```{r setup, message = F, warning = F, results = 'hide'}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, fig.path = 'figs/', dev.args = list(family = 'serif'))

library(tidyverse)
library(patchwork)
library(ggbeeswarm)
library(psycho)
library(lmerTest)
library(hrbrthemes)
library(kableExtra)
library(shiny)

source('R/funcs.R')

data(allexp)
data(bymods)
data(wtmods)
```

## Number of folds {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Number of folds'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Number of irregularites {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Number of irregularities'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Total observations (dissolution) {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Total observations'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Dissolution score {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Dissolution score (0-3)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Shell weight {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Shell weight (g)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Tissue weight {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Tissue weight (g)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Whole weight {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Whole weight (g)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Delta length {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Delta length (cm)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```


## Delta width {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Delta width (cm)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Length rate {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Length rate (cm/d)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Width rate {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Width rate (cm/d)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Final length {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Final length (cm)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```


## Final width {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Final width (cm)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

## Respiration {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Respiration (umol/hr/g)'

toplo <- allexp %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models by week

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
bymods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar) %>% 
  pull(plomod)
```

### Models with week

#### Olympia oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Olympia') %>% 
  filter(var == yvar)

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Olympia') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```

#### Pacific oyster

```{r}
dat <- wtmods %>% 
  filter(species == 'Pacific') %>% 
  filter(var == yvar)
         
dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomodnoint) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week + treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML

dat %>% 
  filter(species == 'Pacific') %>% 
  pull(anomod) %>% 
  .[[1]] %>% 
  knitr::kable(format = 'html', digits = 2, caption = paste0(yvar, ' vs week x treatment')) %>%
  kable_styling(full_width = T, font_size = 14) %>% 
  HTML
```

```{r, fig.height = 5, fig.width = 6, out.width = '70%', results = 'hide', fig.align = 'center'}
dat %>% 
  pull(plomod)
```
