---
output: 
  html_document:
    code_folding: hide
    css: styles.css
---
  
# Evaluation of Oyster exposure experiments {.tabset}
  
```{r setup, message = F, warning = F, results = 'hide'}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, fig.path = 'figs/', dev.args = list(family = 'serif'))

library(tidyverse)
library(patchwork)
library(ggbeeswarm)
library(psycho)
library(lmerTest)
library(hrbrthemes)

source('R/funcs.R')

data(allres)
data(resmods)
data(alldis)
data(dismods)
```

## Respiration {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}

p <- ggplot(allres, aes(x = factor(week), y = resp, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = 'Respiration (umol/hr/g)')

p
```

### Models

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
resmods %>% 
  filter(species == 'Olympia') %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
resmods %>% 
  filter(species == 'Pacific') %>% 
  pull(plomod)
```

## Dissolution score {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Dissolution score (0-3)'
toplo <- alldis %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models 

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
dismods %>% 
  filter(species == 'Olympia') %>% 
  filter(var %in% yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
dismods %>% 
  filter(species == 'Pacific') %>% 
  filter(var %in% yvar) %>% 
  pull(plomod)
```

## Number of folds {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Number of folds'
toplo <- alldis %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models 

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
dismods %>% 
  filter(species == 'Olympia') %>% 
  filter(var %in% yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
dismods %>% 
  filter(species == 'Pacific') %>% 
  filter(var %in% yvar) %>% 
  pull(plomod)
```

## Number of irregularities {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Number of irregularities'
toplo <- alldis %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models 

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
dismods %>% 
  filter(species == 'Olympia') %>% 
  filter(var %in% yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
dismods %>% 
  filter(species == 'Pacific') %>% 
  filter(var %in% yvar) %>% 
  pull(plomod)
```

## Total dissolution observations {.tabset .tabset-pills}

### Raw data

```{r, fig.height= 8, fig.width = 5, fig.align = 'center', out.width = '65%'}
yvar <- 'Total observations'
toplo <- alldis %>% 
  filter(var %in% yvar)

p <- ggplot(toplo, aes(x = factor(week), y = val, colour = species, fill = species)) + 
  geom_boxplot(outlier.shape = NA, alpha = 0.1) + 
  geom_point(aes(group = species), position = position_jitterdodge(jitter.width = 0.1), size = 2, alpha = 0.6) + 
  theme_ipsum_rc() + 
  facet_grid(trt~ .) + 
  scale_colour_ipsum() + 
  scale_fill_ipsum() + 
  theme(legend.title = element_blank()) + 
  labs(x = 'Exposure week', y = yvar)

p
```

### Models 

#### Olympia oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
dismods %>% 
  filter(species == 'Olympia') %>% 
  filter(var %in% yvar) %>% 
  pull(plomod)
```

#### Pacific oyster

```{r, fig.height = 5, fig.width = 10, out.width = '90%', results = 'hide'}
dismods %>% 
  filter(species == 'Pacific') %>% 
  filter(var %in% yvar) %>% 
  pull(plomod)
```